---
title: "Introduction to geojsonlint"
author: "Scott Chamberlain and Andy Teucher"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to geojsonlint}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE
)
```

Tools for linting 'GeoJSON'.

GeoJSON linters available in `geojsonlint`

* `geojson_hint()` - [GeoJSON hint JS library](https://www.npmjs.com/package/geojsonhint)
* `geojson_validate()` - [is-my-json-valid JS library](https://www.npmjs.com/package/is-my-json-valid) using a GeoJSON
schema from [https://github.com/SchemaStore/schemastore](https://github.com/SchemaStore/schemastore)

## Install

Stable version from CRAN

```{r eval=FALSE}
install.packages("geojsonlint")
```

Development version from GitHub

```{r eval=FALSE}
remotes::install_github("ropensci/geojsonlint")
```

```{r}
library("geojsonlint")
```

## Good GeoJSON

geojsonhint JS library

```{r}
geojson_hint(x = '{"type": "Point", "coordinates": [-100, 80]}')
```

is-my-json-valid JS library

```{r}
geojson_validate(x = '{"type": "Point", "coordinates": [-100, 80]}')
```

## Bad GeoJSON

geojsonhint JS library

```{r}
geojson_hint('{"type": "FooBar"}')
```

is-my-json-valid JS library

```{r}
geojson_validate('{ "type": "FeatureCollection" }')
```

## Bad GeoJSON - with reason for failure

geojsonhint JS library

```{r}
geojson_hint('{"type": "FooBar"}', inform = TRUE)
```

is-my-json-valid JS library

```{r}
geojson_validate('{ "type": "FeatureCollection" }', inform = TRUE)
```

## Bad GeoJSON - stop on validation failure

geojsonhint JS library

```{r eval=FALSE}
geojson_hint('{"type": "FooBar"}', error = TRUE)
#> Error: Line 1
#>    - The type FooBar is unknown
```

is-my-json-valid JS library

```{r eval=FALSE}
geojson_validate('{ "type": "FeatureCollection" }', error = TRUE)
#> Error: 1 error validating json:
#> 	- data: no (or more than one) schemas match
```
